Investigations of the galaxies of the LCV

### 2023-05-24 presentation.tex
presentation
-presentation
-made the fsolve give only positive values
-found A_del->weird SFR

% Created 2023-04-30 Sun 20:08
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{breakcites}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{biblatex}
\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage{tgbonum}
\let\itemize\compactitem
\let\description\compactdesc
\let\enumerate\compactenum
\author{Dimitrios Papachistopoulos}
\date{\today}
\title{Investigations of the galaxies of the LCV}
\hypersetup{
 pdfauthor={Dimitrios Papachistopoulos},
 pdftitle={Investigations of the galaxies of the LCV},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
 pdflang={English}}
\begin{document}

@@

\subsection{{\bfseries\sffamily TODO} no indent}
\label{sec:org8d9b93a}
\subsection{{\bfseries\sffamily TODO} fullstops}
\label{sec:orgde0c807}
\subsection{{\bfseries\sffamily TODO} Units in the plots}
\label{sec:org1a3080c}

\begin{abstract}
The paper investigates the properties of galaxies in the Local Cosmological Volume (LCV), using the Catalogue of Neighboring Galaxies\autocite{karachentsevUPDATEDNEARBYGALAXY2013} and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}. The properties studied include the galaxy types, their various masses, the star formation rates (SFRs) and the star formation timescale \(\tau\), gas depletion timescale \(\tau_g\) and the star formation time \(t_{sf}\). The paper aims to understand the distribution and correlation of these properties in the sample of galaxies in the LCV, and how they relate to current astrophysical theories.
\end{abstract}

\section{The Galaxies in the Local Cosmological Volume (LCV)}
\label{sec:org120a319}

The Catalogue of Neigbouring Galaxies (Karachentsev, Igor D. and Makarov  et al. 2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}  are used to extract the B-band, FUV $\backslash$& K-band luminosities\footnote{We use the FUV and B measurments to calculate the B-FUV color index.} , the types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of \(\approx 11\) Mpc. Some of those values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248. From the remaing galaxies we have

\begin{center}
\begin{tabular}{lr}
Measurment & Number of Galaxies\\[0pt]
\hline
Name & 793\\[0pt]
FUVmag & 687\\[0pt]
TType & 793\\[0pt]
Tdw1 & 580\\[0pt]
Tdw2 & 568\\[0pt]
Bmag & 790\\[0pt]
SFR\textsubscript{Ha} & 566\\[0pt]
SFR\textsubscript{FUV} & 688\\[0pt]
K & 789\\[0pt]
MHI & 643\\[0pt]
color & 686\\[0pt]
\end{tabular}
\end{center}

The K-band values are converted to the total Stellar Masses of each galaxy according to the mass-to-light ratio of 0.6 (\cite{lelliSPARCMASSMODELS2016}), and the \(M_{HI}\) can be converted to the total mass of the gas of the galaxy using the equation \(M_g=1.33\,M_{HI}\)

The total SFR of each galaxy can be calcuated by

$$
    SFR_o=\frac{SFR_{FUV}+SFR_{Ha}}{2}
$$
\noindent
if both \(SFR_{H\alpha},SFR_{FUV}\) measurments are available. If only one only one of them is given, then the SFR is equal to the given SFR value

$$
    SFR_o=SFR_i,\ \text{if } SFR_j=0,i\neq j,\ i,j=FUV, H_a
$$

The condition \(SFR_o\geq 10^{-3}M_\odot yr^{-1}\) leaves 579
galaxies. This condition is applied due to the reasons given in the P. Kroupa,M. Haslbauer, I. Banik, S. T. Nagesh and J. Pflamm-Altenburg et al. 2020 \cite{kroupaConstraintsStarFormation2020}

\section{Types of galaxies}
\label{sec:orgd4afc9c}

Using the dataset of 1248 galaxies, do before using the condition and removing the galaxies with the flags, the below histograms can be plotted.

Most of the galaxies in the LCV are Irregular galaxies followed by lenticular galaxies

Out of the 1248 galaxies the 1022 are dwarf galaxies
RODO

\subsection{{\bfseries\sffamily TODO} write a table with the types}
\label{sec:org6c7eaf8}

Most dwarf galaxies have low brightness and are irregulars followed by Dwarf spheroidal.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/hist-Tdw2.png}
\caption{\label{Types of dwarf galaxies brightness}Dwarf galaxy surface brightness morphology, where: H = high; N = normal; L = low; X = extremely low.}
\end{figure}

\section{Delayed-\(\tau\) model}
\label{sec:orgee2851e}

According to P. Kroupa et al. 2020\autocite{kroupaConstraintsStarFormation2020} current star formation rates of galaxies can be described by the 'delayed-\(\tau\)' model as

@@

\noindent
where \(\tau\) is the star formation time-scale,  \(t_{sf}\) is the real time of star formation in a given galaxy and \(A_{del}\) a normalization constant.

@@

\begin{equation}\label{eq:av_SFR M*}
    \overline{SFR}=\frac{\zeta M_*}{t_{sf}}
\end{equation}
where \(\zeta\) accommodates for mass-loss through stella evolution and \(\zeta\approx 1.3\)

@@

\subsection{Constant \(t_{sf}\)}
\label{sec:orgd5bd959}
The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).

@@

can be solved numerically for \(x\) and using the equations (\Ref{eq:SFR}) and (\Ref{eq:av_SFR-x}) the \(A_{del}\) and \(\tau\) of each galaxy are found.

\begin{table}[hc]
\centering
\begin{tabular}{lrrr}
\toprule
{} &    A\_tsf &      tau &    x\_tsf \\
\midrule
count & 5.78E+02 & 5.79E+02 & 5.79E+02 \\
mean  & 2.25E+12 & 1.09E+11 & 1.85E+00 \\
std   & 3.94E+13 & 1.04E+12 & 1.48E+00 \\
min   & 2.48E+07 & 1.93E+09 & 5.59E-04 \\
25\%   & 1.41E+08 & 4.18E+09 & 5.65E-01 \\
50\%   & 6.84E+08 & 7.79E+09 & 1.60E+00 \\
75\%   & 5.70E+09 & 2.21E+10 & 2.99E+00 \\
max   & 9.10E+14 & 2.24E+13 & 6.47E+00 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMt-log_A_tsf-color_x_tsf.png}
\caption{\label{fig:A_tsf_Mt}Total Mass \(M_t\) - \(A_{del}|_{t_{sf}}\)}
\end{figure}
\begin{equation}\label{eq:logMt-log_A_tsf-color_x_tsf}
\begin{align}
& $log(A_{del}|_t_{sf}) = (9.6(4) \times 10^{-1})\cdot $log(M_t)$ + (8(4) \times 10^{-1}) \\ 
& \textrm{with correlation } R^2=48\%
\end{align}
\end{equation}
\noindent

\subsection{Constant \(\tau\)}
\label{sec:org46757ea}

Assuming for an constant \(\tau=3.5\) Gyr, we cannot use the same \(\overline{SFR}\) since it depends on \(t_{sf}\). Using the equations\textasciitilde{}(\Ref{eq:av_SFR M*}) and (\Ref{eq:ratio})

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logStellarMass-log_A_tau-color_x_tau.png}
\caption{\label{fig:A_tau_Mt}Total Mass \(M_t\) - \(A_{del}|_{\tau}\)}
\end{figure}
\begin{equation}\label{eq:logStellarMass-log_A_tau-color_x_tau}
\begin{align}
& $log(A_{del}|_\tau) = (8.74(12) \times 10^{-1})\cdot $log(M_t)$ + (1.31(10) \times 10^{0}) \\ 
& \textrm{with correlation } R^2=90\%
\end{align}
\end{equation}
\noindent

\subsection{Comparing the two results}
\label{sec:org62d708b}

\subsubsection{Comparing the \(x\)'s}
\label{sec:org7a303ba}

Comparing the two different results for x, we see that the \(x|_\tau\) has a lower \(\sigma\)

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/Comparing_the_x_Mt.png}
\caption{\label{fig:Comparing the two x's, According to their total masses}Comparing the two x's, According to their total masses}
\end{figure}
\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/x_tau-Mt-color.png}
\caption{\label{fig:$x|_\tau=f(M_t)$, with their color index}\(x|_\tau=f(M_t)\), with their color index}
\end{figure}

@@

The two results are interrelated through the equation:
\begin{equation}\label{eq:x_tsf-x_tau}
\begin{align}
& x|_\tau = (6.30(6) \times 10^{-1})\cdot x|_{tsf} + (1.374(15) \times 10^{0}) \\ 
& \textrm{with correlation } R^2=94\%
\end{align}
\end{equation}
\noindent

@@

\begin{enumerate}
\item The galaxies with a higher total mass deviate less from the linear fit and are older.
\item The younger galaxies are mainly later types of galaxies
\item For lower x's, the galaxies have a lower color index which indicates that they are younger. So the values are inline with the experimental values.
\end{enumerate}

\subsubsection{Comparing the normalization constants}
\label{sec:org4a59895}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/Comparing_the_A_x.png}
\caption{\label{fig:Comparing the two A_{del}}Comparing the two A\textsubscript{del}}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/A_tau-A_tsf_colo_X.png}
\caption{\label{fig:Comparison of the 2 A_{del}s according to their $x$}Comparison of the 2 A\textsubscript{del}s according to their \(x\)}
\end{figure}
\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/A_tau-A_tsf_Mt.png}
\caption{\label{fig:Comparison of the 2 A_{del}s according to their total masses}Comparison of the 2 A\textsubscript{del}s according to their total masses}
\end{figure}

For high \(x\) and high masses the two A\textsubscript{del}s have a high correlation. Specifically:
\begin{enumerate}
\item For high \(x\) the \(A_{del}|_{\tau}-A_{del}|_{t_{sf}}\) plot follows a \(y=x\) trend, which means that for older stars and stars with a low star formation timescale \(\tau\), the normalization constant is the same despite the method used to calculate it.
\item The same is true for more massive galaxies, since they deviate less from the \(y=x\) line
\end{enumerate}

\subsubsection{Trying to make the A\textsubscript{del} cloud more compact}
\label{sec:org4bf81bb}

Having found \(x|_{t_sf}\) and \(x|_{\tau}\) we can find a relation between these two values

@@

\subsection{Int SFR to find the A\textsubscript{del}}
\label{sec:org6350c57}

If we integrate equation (\ref{eq:SFR}) we get:

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/log_A_theor_tau-logStellarMass-color_x_tsf.png}
\caption{\label{fig:Comparison of the A_del according to their Stellar Mass}Comparison of the A\textsubscript{del} according to their Stellar Mass}
\end{figure}

\section{The gas depletion timescale \(\tau_g\) \label{SEC:tau_g}}
\label{sec:org325e6be}

The gas depletion timescale \(\tau_g\) measures the time taken by a galaxy to exhaust its gas content Mg given the current SFR\autocites{nageshSimulationsStarformingMainsequence2023}[][]{pflamm-altenburgFundamentalGasDepletion2009}.
\begin{equation}\label{eq:tau_g}
\tau_g=\frac{M_g}{\dot{M_*}}=\frac{M_g}{SFR}
\end{equation}

@@

Despite a weak logarithmic correlation (as indicated by \(R^2 = 32\%\) \noindent), there is a noticeable trend of decreasing \(\tau_g\) with increasing SFR and \(M_g\).

@@

The logarithmic correlation between \(\tau_g-M_*\) is low (\(R^2 = 21\%\) \noindent), there seems to be a pattern wherein the decrease of \(\tau_g\) corresponds to an increase in the values of the Stellar Mass, but there does not seem to be one for \(\tau_g-\tau\)

@@

Again it can be observed that as the \(\tau_g\) decreases, the corresponding values of \(M_t\) increase, but the logarithmic correlation is again low (\(R^2 = 11\%\) \noindent), and there is no clear correlation between \(\tau_g-t_{sf}\)

There is a notable trend, wherein for high masses we have a shorter timescale.

\section{Mass relations}
\label{sec:org2e3fc57}

Many of the galaxies masses have a high correlation with each other, and also help us understand the previous calculations.

@@

For the plot \ref{fig:mg_SMass}:
\begin{equation}\label{eq:logMg-logStellarMass}
\begin{align}
& $M_g$ = (1.098(35) \times 10^{0})\cdot $M_*$ + (-7.9(2.9) \times 10^{-1}) \\ 
& \textrm{with correlation } R^2=64\%
\end{align}
\end{equation}
\noindent

@@

For the plot \ref{fig:SMass_mt}:
\begin{equation}\label{eq:logStellarMass-logMt}
\begin{align}
& $M_t$ = (8.41(9) \times 10^{-1})\cdot $M_*$ + (1.69(8) \times 10^{0}) \\ 
& \textrm{with correlation } R^2=94\%
\end{align}
\end{equation}
\noindent

@@

For the plot \ref{fig:mg_mt}:
\begin{equation}\label{eq:logMg-logMt-color_log_SFR_0}
\begin{align}
& $M_t$ = (1.065(23) \times 10^{0})\cdot $M_g$ + (-1.5(1.9) \times 10^{-1}) \\ 
& \textrm{with correlation } R^2=81\%
\end{align}
\end{equation}
\noindent

@@

The \(M_t-M_*\) (\ref{fig:SMass_mt}) plot is particularly noteworthy, displaying a correlation  of \(R^2 = 94\%\) \noindent. This plot also indicates that galaxies with greater total and stellar masses tend to have higher SFR, consistent with the findings in section \ref{SEC:tau_g} where \(\tau_g\) decreases with increasing masses.

@@

From the \ref{fig:col_Mr}, we conclude that when the color index is higher the Mass ratio decreases, which is to be expected, since the higher the B-FUV the more active the star formation of the galaxy.

\section{Variations in Star Formation Rate Across the Different Masses}
\label{sec:orgb7febe7}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-color.png}
\caption{\label{fig:None}None}
\end{figure}

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-log_tau_g-color_logStellarMass.png}
\caption{\label{fig:None}None}
\end{figure}
\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMt-log_SFR_0-color_log_tau_g.png}
\caption{\label{fig:None}None}
\end{figure}
(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7f3d4e77b190>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
\includegraphics[width=.9\linewidth]{./figs/logMt-log_tau-color_log_tau_g.png}
\end{center}', 'logMt-log\textsubscript{tau}-color\textsubscript{log}\textsubscript{tau}\textsubscript{g}')

\subsection{{\bfseries\sffamily TODO} put that tau and tsf dont have a correlation with Mt}
\label{sec:org5dfe35c}

\pagebreak
\printbibliography
\end{document}

>>>>

% Created 2023-05-11 Thu 16:48
% Intended LaTeX compiler: pdflatex
\documentclass[presentation]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usetheme{default}
\usecolortheme{}
\usefonttheme{}
\useinnertheme{}
\useoutertheme{}
\author{Dimitrios Papachistopoulos}
\date{\today}
\title{Investigations of the galaxies of the LCV}

\hypersetup{
 pdfauthor={Dimitrios Papachistopoulos},
 pdftitle={Investigations of the galaxies of the LCV},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
 pdflang={English}}
\usepackage{biblatex}
\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
\begin{document}

@@

\begin{frame}[label={sec:org9d0b2d9}]{Abstract}
\begin{block}{LCV}
The paper investigates the properties of galaxies in the Local Cosmological Volume (LCV), using the Catalogue of Neighboring Galaxies\autocite{karachentsevUPDATEDNEARBYGALAXY2013} and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}.
\end{block}
\begin{block}{The studied properties}
\begin{enumerate}
\item Galaxy types,
\item Their various masses,
\item The star formation rates (SFRs)
\item Timescales
\begin{enumerate}
\item Star formation timescale \(\tau\),
\item Gas depletion timescale \(\tau_g\)
\item The star formation time \(t_{sf}\).
\end{enumerate}
\end{enumerate}
\end{block}
\begin{block}{Goal}
The paper aims to understand the distribution and correlation of these properties in the sample of galaxies in the LCV, and how they relate to current astrophysical theories.
\end{block}
\end{frame}

\begin{frame}[label={sec:org75f05ef}]{The Galaxies in the Local Cosmological Volume (LCV)}
The Catalogue of Neigbouring Galaxies (Karachentsev, Igor D. and Makarov  et al. 2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}  are used

\begin{block}{Data}
\begin{enumerate}
\item The B-band, FUV \& K-band luminosities\footnote{We use the FUV and B measurments to calculate the B-FUV color index.} ,
\item The types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s,
\item Masses:
\begin{enumerate}
\item The mass within the Holmberg radius (M26)\footnote{\uline{Definition} \alert{Holmberg radius}: \texttt{A convenient measure of the optical extent of a galaxy is the /Holmberg radius/ (Holmberg 1958), which is the major-axis radius at a surface brightness of 26.5 photographic mag arcsec-2}\autocite{MassesMasstoLightRatios}},
\end{enumerate}
\begin{enumerate}
\item The Hydrogen masses of the galaxies (\(M_{HI}\))
\end{enumerate}
\item Their SFRs based on integrated  H and far-ultraviolet (FUV) measurments
\end{enumerate}

\begin{enumerate}
\item The galaxies are within a distance of \(\approx 11\) Mpc.
\item Some of those values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248
\end{enumerate}

\begin{center}
\begin{tabular}{|l|l|}
\hline
Measurment & Number of Galaxies \\
\hline
Name & 793 \\
FUVmag & 687 \\
TType & 793 \\
Tdw1 & 580 \\
Tdw2 & 568 \\
Bmag & 790 \\
SFR$\backslash$\_Ha & 566 \\
SFR$\backslash$\_FUV & 688 \\
K & 789 \\
MHI & 643 \\
color & 686 \\
\hline
\end{tabular}
\end{center}

\begin{enumerate}
\item The K-band values are converted to the total Stellar Masses of each galaxy according to the mass-to-light ratio\autocite{lelliSPARCMASSMODELS2016}
$$\frac{M_*}{K}=0.6$$
\item The \(M_{HI}\) can be converted to the total mass of the gas of the galaxy using the equation $$M_g=1.33\cdot M_{HI}$$
\end{enumerate}
\begin{enumerate}
\item The total SFR of each galaxy can be calcuated by
\end{enumerate}

$$
    SFR_o=\frac{SFR_{FUV}+SFR_{Ha}}{2}
$$

$$
    SFR_o=SFR_i,\ \text{if } SFR_j=0,i\neq j,\ i,j=FUV, H_a
$$
\begin{enumerate}
\item We use the FUV and B measurments to calculate the B-FUV color index.
\end{enumerate}

The condition \(SFR_o\geq 10^{-3}M_\odot yr^{-1}\) leaves 579 galaxies. This condition is applied due to the reasons given in the P. Kroupa,M. Haslbauer, I. Banik, S. T. Nagesh and J. Pflamm-Altenburg et al. 2020 \cite{kroupaConstraintsStarFormation2020}
\end{block}
\end{frame}

\begin{frame}[label={sec:org236576b}]{Types of galaxies}
Using the dataset of 1248 galaxies, do before using the condition and removing the galaxies with the flags, the below histograms can be plotted.

\begin{itemize}
\item Most of the galaxies in the LCV are Irregular galaxies followed by lenticular galaxies

\item Out of the 1248 galaxies the 1022 are dwarf galaxies

\item Most dwarf galaxies have low brightness and are irregulars followed by Dwarf spheroidal.
\end{itemize}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/hist-Tdw2.png}
\caption{\label{Types of dwarf galaxies brightness}Dwarf galaxy surface brightness morphology, where: H = high; N = normal; L = low; X = extremely low.}
\end{figure}
\end{frame}

\begin{frame}[label={sec:org05089e9}]{Delayed-\(\tau\) model}
According to P. Kroupa et al. 2020\autocite{kroupaConstraintsStarFormation2020} current star formation rates of galaxies can be described by the 'delayed-\(\tau\)' model as

@@

where \(\tau\) is the star formation time-scale,  \(t_{sf}\) is the real time of star formation in a given galaxy and \(A_{del}\) a normalization constant.

@@

\begin{equation}\label{eq:av_SFR M*}
    \overline{SFR}=\frac{\zeta M_*}{t_{sf}}, \zeta = \approx 1.3
\end{equation}

where \(\zeta\) accommodates for mass-loss through stellar evolution

@@

\begin{enumerate}
\item Constant \(t_{sf}\)
\item Constant \(\tau\)
\item Integrate the SFR to find the A\textsubscript{del}
\end{enumerate}

\begin{block}{Constant \(t_{sf}\)}
The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).

@@

can be solved numerically for \(x\) and using the equations (\ref{eq:SFR}) and (\ref{eq:av_SFR-x}) the \(A_{del}\) and \(\tau\) of each galaxy are found.

\begin{center}
\begin{tabular}{lrrr}
 & A\textsubscript{tsf} & tau & x\textsubscript{tsf}\\[0pt]
\hline
count & 578 & 579 & 579\\[0pt]
mean & 2.24715e+12 & 1.08958e+11 & 1.85344\\[0pt]
std & 3.93675e+13 & 1.04132e+12 & 1.4763\\[0pt]
min & 2.47798e+07 & 1.93205e+09 & 0.000558601\\[0pt]
25\% & 1.40573e+08 & 4.18098e+09 & 0.564779\\[0pt]
50\% & 6.83764e+08 & 7.79265e+09 & 1.60408\\[0pt]
75\% & 5.70379e+09 & 2.21327e+10 & 2.98973\\[0pt]
max & 9.10088e+14 & 2.23774e+13 & 6.46982\\[0pt]
\end{tabular}
\end{center}

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMt-log_A_tsf-color_x_tsf.png}
\caption{\label{fig:A_tsf_Mt}Total Mass \(M_t\) - \(A_{del}|_{t_{sf}}\)}
\end{figure}

\begin{equation}\label{eq:logMt-log_A_tsf-color_x_tsf}
\begin{align}
& $log(A_{del}|_t_{sf}) = (9.6(4) \times 10^{-1})\cdot $log(M_t)$ + (8(4) \times 10^{-1}) \\
& \textrm{with correlation } R^2=48\%
\end{align}
\end{equation}
\noindent
\end{block}

\begin{block}{Constant \(\tau\)}
Assuming for an constant \(\tau=3.5\) Gyr, we cannot use the same \(\overline{SFR}\) since it depends on \(t_{sf}\). Using the equations\textasciitilde{}(\Ref{eq:av_SFR M*}) and (\Ref{eq:ratio})

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logStellarMass-log_A_tau-color_x_tau.png}
\caption{\label{fig:A_tau_Mt}Total Mass \(M_t\) - \(A_{del}|_{\tau}\)}
\end{figure}

\begin{equation}\label{eq:logStellarMass-log_A_tau-color_x_tau}
\begin{align}
& $log(A_{del}|_\tau) = (8.74(12) \times 10^{-1})\cdot $log(M_t)$ + (1.31(10) \times 10^{0}) \\
& \textrm{with correlation } R^2=90\%
\end{align}
\end{equation}
\noindent
\end{block}

\begin{block}{Comparing the two results}
\begin{block}{Comparing the \(x\)'s}
Comparing the two different results for x, we see that the \(x|_\tau\) has a lower \(\sigma\)

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/Comparing_the_x_Mt.png}
\caption{\label{fig:Comparing the two x's, According to their total masses}Comparing the two x's, According to their total masses}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/x_tau-Mt-color.png}
\caption{\label{fig:$x|_\tau=f(M_t)$, with their color index}\(x|_\tau=f(M_t)\), with their color index}
\end{figure}

@@

The two results are interrelated through the equation:

\begin{equation}\label{eq:x_tsf-x_tau}
\begin{align}
& x|_\tau = (6.30(6) \times 10^{-1})\cdot x|_{tsf} + (1.374(15) \times 10^{0}) \\
& \textrm{with correlation } R^2=94\%
\end{align}
\end{equation}
\noindent

@@

\begin{enumerate}
\item The galaxies with a higher total mass deviate less from the linear fit and are older.
\item The younger galaxies are mainly later types of galaxies
\item For lower x's, the galaxies have a lower color index which indicates that they are younger. So the values are inline with the experimental values.
\end{enumerate}
\end{block}

\begin{block}{Comparing the normalization constants}
\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/Comparing_the_A_x.png}
\caption{\label{fig:Comparing the two A_{del}}Comparing the two A\textsubscript{del}}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/A_tau-A_tsf_colo_X.png}
\caption{\label{fig:Comparison of the 2 A_{del}s according to their $x$}Comparison of the 2 A\textsubscript{del}s according to their \(x\)}
\end{figure}

@@

For high \(x\) and high masses the two A\textsubscript{del}s have a high correlation. Specifically:
\begin{enumerate}
\item For high \(x\) the \(A_{del}|_{\tau}-A_{del}|_{t_{sf}}\) plot follows a \(y=x\) trend, which means that for older stars and stars with a low star formation timescale \(\tau\), the normalization constant is the same despite the method used to calculate it.
\item The same is true for more massive galaxies, since they deviate less from the \(y=x\) line
\end{enumerate}
\end{block}

\begin{block}{Trying to make the A\textsubscript{del} cloud more compact}
Having found \(x|_{t_sf}\) and \(x|_{\tau}\) we can find a relation between these two values

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/A_tau-A_tsf_Mt.png}
\caption{\label{fig:Comparison of the 2 A_{del}s according to their total masses}Comparison of the 2 A\textsubscript{del}s according to their total masses}
\end{figure}
\end{block}
\end{block}

\begin{block}{Int SFR to find the A\textsubscript{del}}
If we integrate equation (\ref{eq:SFR}) we get:

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/log_A_theor_tau-logStellarMass-color_x_tsf.png}
\caption{\label{fig:Comparison of the A_del according to their Stellar Mass}Comparison of the A\textsubscript{del} according to their Stellar Mass}
\end{figure}
\end{block}
\end{frame}

\begin{frame}[label={sec:org40e1c03}]{The gas depletion timescale \(\tau_g\) \label{SEC:tau_g}}
The gas depletion timescale \(\tau_g\) measures the time taken by a galaxy to exhaust its gas content Mg given the current SFR\autocites{nageshSimulationsStarformingMainsequence2023}[][]{pflamm-altenburgFundamentalGasDepletion2009}.
\begin{equation}\label{eq:tau_g}
\tau_g=\frac{M_g}{\dot{M_*}}=\frac{M_g}{SFR}
\end{equation}

@@

Despite a weak logarithmic correlation (as indicated by ==), there is a noticeable trend of decreasing \(\tau_g\) with increasing SFR and \(M_g\).

@@

The logarithmic correlation between \(\tau_g-M_*\) is low (==), there seems to be a pattern wherein the decrease of \(\tau_g\) corresponds to an increase in the values of the Stellar Mass, but there does not seem to be one for \(\tau_g-\tau\)

@@

Again it can be observed that as the \(\tau_g\) decreases, the corresponding values of \(M_t\) increase, but the logarithmic correlation is again low (==), and there is no clear correlation between \(\tau_g-t_{sf}\)

There is a notable trend, wherein for high masses we have a shorter timescale.
\end{frame}

\begin{frame}[label={sec:orgfa6d8ce}]{Mass relations}
Many of the galaxies masses have a high correlation with each other, and also help us understand the previous calculations.

@@

For the plot \ref{fig:mg_SMass}:

\begin{equation}\label{eq:logMg-logStellarMass}
\begin{align}
& $M_g$ = (1.098(35) \times 10^{0})\cdot $M_*$ + (-7.9(2.9) \times 10^{-1}) \\
& \textrm{with correlation } R^2=64\%
\end{align}
\end{equation}
\noindent

@@

For the plot \ref{fig:SMass_mt}:

\begin{equation}\label{eq:logStellarMass-logMt}
\begin{align}
& $M_t$ = (8.41(9) \times 10^{-1})\cdot $M_*$ + (1.69(8) \times 10^{0}) \\
& \textrm{with correlation } R^2=94\%
\end{align}
\end{equation}
\noindent

@@

For the plot \ref{fig:mg_mt}:

\begin{equation}\label{eq:logMg-logMt-color_log_SFR_0}
\begin{align}
& $M_t$ = (1.065(23) \times 10^{0})\cdot $M_g$ + (-1.5(1.9) \times 10^{-1}) \\
& \textrm{with correlation } R^2=81\%
\end{align}
\end{equation}
\noindent

@@

The \(M_t-M_*\) (\ref{fig:SMass_mt}) plot is particularly noteworthy, displaying a correlation  of ==. This plot also indicates that galaxies with greater total and stellar masses tend to have higher SFR, consistent with the findings in section \ref{SEC:tau_g} where \(\tau_g\) decreases with increasing masses.

@@

From the \ref{fig:col_Mr}, we conclude that when the color index is higher the Mass ratio decreases, which is to be expected, since the higher the B-FUV the more active the star formation of the galaxy.
\end{frame}

\begin{frame}[label={sec:orgbd7dd9c}]{Variations in Star Formation Rate Across the Different Masses}
\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-color.png}
\caption{\label{fig:None}None}
\end{figure}

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-log_tau_g-color_logStellarMass.png}
\caption{\label{fig:None}None}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMt-log_SFR_0-color_log_tau_g.png}
\caption{\label{fig:None}None}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMt-log_tau-color_log_tau_g.png}
\caption{\label{fig:None}None}
\end{figure}'

\begin{block}{put that tau and tsf dont have a correlation with Mt}
\pagebreak
\printbibliography
\end{block}
\end{frame}
\end{document}
